Adaptive broadcast tree for multicores

### 2013-04-29 paper.tex
Explanation of aggregation

Similarly to what has been done in wireless sensor networks (where it
also matters to reduce the number of messages, but other reasons:
power consumption), we can do aggregation in nodes. In difference to
traditional distributed systems, this works, because it is easy to
deploy custom software on every node in the network. Classical
distributed systems do not typically allow this. Furthermore, reducing
the number of messages at the price of higher complexity does not make
sense there.

>>>>

Aggregation is the act of collecting information from nodes (i.e.\ it
is kind of the reverse of a broadcast). In node on the return path,
information can be aggregated. One example is batching, where several
pieces of information are grouped in the same message to reduce packet
processing overhead. Another example is pre-processing of data. One
example is pre-calculating the average value of child messages if the
sink node is not interested in individual values.

Similarly to what has been done in wireless sensor networks (where it
also matters to reduce the number of messages, but for other reasons:
power consumption), we can do aggregation in nodes. In difference to
traditional distributed systems, this works, because it is easy to
deploy custom software on every node in the network. Classical
distributed systems do not typically allow this. Furthermore, reducing
the number of messages at the price of higher complexity does not make
sense there.
